Hedonic House Prisce Model King County

### 2023-11-19 Msb205/Msb205.qmd
:)

```{r Oppgave 1}
kc_house_data <- read.csv("./Data/kc_house_data.csv")
```

@@

@@

```{r}
mod1 <- KC_husdata "price ~ bedrooms + bathrooms + sqft_living + sqft_living15 + sqft_lot + sqft_lot15 + sqft_above + floors + grade + yr_built + yr_renovated + waterfront + condition + view + dist_cbd_km + EHD_percen + low + high + year_month"
```

@@

```{r}
mod2 <- KC_husdata "price ~ bedrooms + bathrooms + sqft_living + sqft_living15 + sqft_lot + sqft_lot15 + sqft_above + floors + grade + yr_built + yr_renovated + waterfront + condition + view + income + low + mid + high + year_month"
```

>>>>

```{r Oppgave 1}
kc_house_data <- read.csv(Msb205/Data/kc_house_data.csv)

@@

```{r}
# Create the second multiple regression model
mod2 <- lm(price ~ bedrooms + bathrooms + sqft_living + sqft_living15 + sqft_lot + sqft_lot15 + sqft_above + floors + grade + yr_built + yr_renovated + waterfront + condition + view + income + low + mid + high + year_month, data = KC_husdata)

# Print a summary of the second model
summary(mod2)
```

@@

```{r}
mod3 <- lm(price ~ bedrooms + bathrooms + sqft_living + sqft_living15 + sqft_lot + sqft_lot15 + sqft_above + floors + grade + yr_built + yr_renovated + waterfront + condition + view + dist_cbd_km + EHD_percen + low + high + year_month, data = KC_husdata)

# Print a summary of the model
summary(mode3)

@@
